DRAFT: Go Implementation of Techniques for Weighted Language Equivalence

### 2020-10-11 paper/sections/runtime.tex
added tolerance tests, added comments to code. 0 problems in code

%\subsection{Tolerance and F1 Score}
The first runtime result we introduce is the study of the influence 
of the tolerance value choice over the correctness of the algorithms results.
Tests took place on randomly generated automata. A basis of  $\llwb$ was 
computed for each automaton with BPR. An arbitrary number of vector pairs were generated 
as a random linear combination of the vectors in the spanning set of $\llwb$. 
An identical quantity of completely random vector pairs were generated.
BPREquivalence and HKC procedures were then executed with those pairs in input.

@@

\begin{figure}[htbp!]
    \centering
    \includegraphics[width=.8\textwidth]{./plots/f1-tol.pdf}

    \caption{F1 score over tolerance tests, 1000 vector pairs tested per automaton.}
    \label{fig:f1}
\end{figure}

>>>>

%\subsection{Tolerance and F1 Score}
We the studied of the influence 
of the tolerance value over the correctness of the algorithms results.
Tests took place on randomly generated automata. A basis of  $\llwb$ was 
computed for each automaton with BPR. An arbitrary number of vector pairs were generated 
as an uniformly distributed random linear combination of the vectors in the spanning set of $\llwb$. 
The same quantity of vector pairs was generated randomly with an uniform distribution.
BPREquivalence and HKC procedures were then executed with those pairs in input.

@@

\begin{figure}[htbp!]
    \centering
    \includegraphics[width=.75\textwidth]{./plots/f1-tol-1e-06.pdf}
    \includegraphics[width=.75\textwidth]{./plots/f1-tol-1e-13.pdf}
    \caption{F1 score over tolerance tests, 2000 vector pairs tested per automaton.}
    \label{fig:f1}
\end{figure}

\begin{figure}[htbp!]
    \centering
    \includegraphics[width=.75\textwidth]{./plots/f1-tol-1e-16.pdf}
    \includegraphics[width=.75\textwidth]{./plots/f1-tol-1e-20.pdf}
    \caption{F1 score over tolerance tests, 2000 vector pairs tested per automaton.}
    \label{fig:f1-2}
\end{figure}
